\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
% \usepackage[a4paper, total={6.5in, 9.5in}]{geometry}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingg}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Aarush Bhat} \\ \vspace{8pt}
    % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small 
    \href{mailto:hey@sloorush.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{hey@sloorush.com}} ~ 
    \href{https://sloorush.com}{\raisebox{-0.2\height}\faLink\   \underline{sloorush.com}} ~
    \href{tel://+919977955466}{\raisebox{-0.2\height}\faPhone\   \underline{+91 9977955466}} ~
    \href{https://linkedin.com/in/aarush-bhat/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/aarush-bhat}}  ~
    \href{https://github.com/sloorush}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/sloorush}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology, Vellore}{Jul 2019 -- Apr 2023 (Expected)}
      {B.Tech in Computer Science and Engineering}{8.29, CGPA}
  \resumeSubHeadingListEnd


%-----------Certification-----------
% \section{Certifications}
%   \resumeSubHeadingListStart
%     \resumeSubheadingg
%       {Certified Kubernetes Administrator, Linux Foundation}{Jul 2022}
%   \resumeSubHeadingListEnd
  
%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     \resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

 \resumeSubheadingg
      {\href{https://summerofcode.withgoogle.com/}{Google Summer of Code}}{May 2021 -- Present}
      \resumeItemListStart
        \resumeItem{Student Mentee at \underline{\href{https://www.github.com/haskell}{Haskell Foundation}}. (Haskell, Compiler Design, Language server, LSP)}
        \resumeItem{Enabling features like Folding Ranges, Semantic Highlighting Etc. for the Haskell Language Server.}
    \resumeItemListEnd
%     \vspace{-10pt}

    \resumeSubheadingg
      {\href{https://www.summerofbitcoin.org/}{Summer of Bitcoin}}{Aug 2021 -- Sept 2021}
      \resumeItemListStart
        \resumeItem{Open source Mentee at \underline{\href{https://www.github.com/utreexo}{MIT-DCI utreexo}} under the mentorship of Calvin Kim and Tadge Dryja. (GoLang, Bitcoin)}
        \resumeItem{Authored support for signet and other significant improvements to help scale bitcoin.}
    \resumeItemListEnd

  \resumeSubheadingg
      {\href{https://twitter.com/thetaskapp}{MSquare Labs}}{May 2021 -- Jul 2021}
      \resumeItemListStart
        \resumeItem{Full stack developer at The Tasks App. (TypeScript, React, SSG, Apple Design System)}
        \resumeItem{Worked with the Design team to create the website and blog for The Task App.}
    \resumeItemListEnd

    \resumeSubheadingg
      {\href{https://byteavenue.org}{Byte Avenue}}{Mar 2020 -- Dec 2020}
      \resumeItemListStart
        \resumeItem{SDE Intern, part of the Frontend Team. (JavaScript, React, Redux, Material UI)}
        \resumeItem{Member of the founding team and worked on the initial iterations of the coding platform.}
    \resumeItemListEnd
    
    \resumeSubheadingg
      {\href{https://byteavenue.org}{CodePark}}{Sept 2019 -- Mar 2020}
      \resumeItemListStart
        \resumeItem{Frontend Developer. (Javascript, React, SCSS)}
        \resumeItem{Worked on the web platform and internal tools and managed marketing campaigns.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/EnchanteHQ/}{Enchante \faGithub}} $|$ \emph{TypeScript, MongoDB, Augmented reality, OAuth, Azure}}{Jul 2021}
          \resumeItemListStart
            \resumeItem{Enchanté is an attempt to reinvent the traditional transaction system and taking contactless payment to a whole new level by adopting bleeding-edge technology such as Augmented reality and nearby payments within eyesight.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/sloorush/ebpf-keylogger}{eBPF Keylogger \faGithub}} $|$ \emph{Python, C, eBPF, Linux}}{Nov 2021}
          \resumeItemListStart
            \resumeItem{Utilizes the power of eBPF to build a keylogger that can be used for monitoring or logging}
            \resumeItem{Built using BCC toolkit to enable creating efficient kernel tracing and manipulation programs.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{\href{https://github.com/DarthBenro008/greencredus}{GreenCredUs \faGithub}} $|$ \emph{JavaScript, Blockchain, Sustainability}}{Feb 2021}
          \resumeItemListStart
            \resumeItem{A carbon credit system implemented on general public to help save the environment.}
            \resumeItem{Implements cryptocurrency built on the Tezos network and an app built over React.js.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------SKILLS AND INTERESTS-----------
\section{Skills and Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{ : JavaScript, TypeScript, Haskell, GoLang, C++, Python, Bash} \\
     \textbf{Databases}{: MongoDB, SQL, Redis} \\
     \textbf{DevOps}{:  AWS, Azure, Docker, Github Actions, Kubernetes} \\
     \textbf{Design}{: Figma, Adobe Lightroom} \\
     \textbf{Blockchain}{: Bitcoin, Ethereum} \\
     \textbf{Languages}{: English, Hindi, French, Kashmiri} \\
     \textbf{Interests}{: Formula 1, Music, Business}
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------LEADERSHIP---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheadingg{{\href{https://ieeevit.org}{IEEE-VIT}}}{Dec 2019 -- Present}
            \resumeItemListStart
                \resumeItem{Technical Head at IEEE-VIT, one of the most active Technical Student bodies representing the IEEE organisation as a chapter on the Vellore Institute Of Technology campus.}
                \resumeItem{Responsible for Technical growth of 70+ members in the organisation inculcating and promoting the Open Source Software culture and good development practices.}
                \resumeItem{Developed software for events and projects used by 15000+ participants in 100+ countries for multiple events.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Achievements-----------
\section{Achievements}
     \resumeItemListStart
        \resumeItem{Won MIT Bitcoin Hack (Cambridge, May 2022), DevSoc (Vellore, April 2021), DevSpace (Vellore, March 2021), and KUHackfest (Kathmandu, Feb 2021).}
\vspace{-6pt}
        \resumeItem{Mentor, \underline{\href{https://www.youtube.com/watch?v=9VDt1iRoiFY}{Speaker}} and Judge at Sparkathon 2021 - A 4-day Hackathon by NMIMS, Navi Mumbai.}
        \vspace{-6pt}
   		\resumeItem{Awarded Distinction in Trinity College London in Rock and Pop Guitar Grade 2(Nov 2016), Trinity College London Rock and Pop Guitar Initial Grade(Nov 2015)}
        \vspace{-6pt}
        \resumeItem{Awarded the CBSE Certificate of Merit for outstanding performance in SSC Examination.}
   \resumeItemListEnd

\end{document}
